\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{scrextend}
\usepackage{lipsum}


 \begin{document}\noindent
 \hspace*{5pt}\textbf{RADHIT DEDANIA}
\newline
 \hspace*{2.5pt} Department of Electrical Engineering
\newline
\hspace*{6pt}Indian Institute of Technology Kanpur, India
\newline
\hspace*{5pt}\textit{Email: radhit@iitk.ac.in}
\vspace{10pt}

\hrule

\vspace{2.5pt}
\hrule
\vspace{5pt}
\noindent My research interests are Artificial Intelligence, Algorithms and Computer Architecture. I want to pursue research in these fields in future.
\vspace{5pt}

\hrule
\vspace{2.5pt}
\hrule
\vspace{5pt} \noindent
 \hspace{5pt} \textbf{Education}
\newline \noindent 

\noindent \vspace*{10pt} \begin{left}
  \begin{tabular}{| c | c | c | c |} 
 \hline
 Matriculation & 2012 & SN Kansagra School & 92.57\%  \\ [0.5ex] 
 \hline
 Intermediate & 2014 & D.A.V Public School & 93.20\% \\ 
 \hline
 BTech & Present & Indian Institute of Technology, Kanpur & 9.22/10  \\
 \hline

\end{tabular}
\end{left}\noindent

\vspace*{5pt} \noindent
\hspace*{5pt} \textbf{Course details}
\newline \noindent 

\noindent \vspace*{10pt} \begin{left}
  \begin{tabular}{| c | c | c |} 
 \hline
  \textbf{Semester} & \textbf{Total Credits} & \textbf{Highlights}  \\ [0.5ex] 
 \hline
 Jan 2016-Apr 2016 & 54 & ESC-101A  \\ [0.5ex] 
 \hline
 Jul 2016-Dec 2016 & 57 & ESO-207A \\ [0.5ex]
 \hline
 Jul 2017-Dec 2017 & 65 & CS-345A\\  [0.5ex]
 \hline
 Jul 2017-Dec 2017 & 65 & CS-771A \\ [0.5ex] 
 \hline


\end{tabular}
\end{left}\noindent 

\vspace*{5pt} \noindent
\hspace*{5pt} \textbf{Skills} \vspace{5pt}

\noindent \hspace*{5pt} Programming Languages : C, C++, Java, Python, Verilog-A \newline \noindent \hspace*{6pt} Platforms / Tools : Linux, Windows, Matlab, GNU Octave, MicroCap, Latex,\newline \hspace*{91pt} AutoCad, SolidWorks

\vspace*{5pt} \noindent
\hspace*{5pt} \textbf{Projects} \vspace{5pt} 

 1. Robust Feature Extraction Using Deep Stacked Autoencoder (SURGE-\noindent \hspace*{27
 pt}2017)
 (Prof. Nishchal Kumar Verma (IITK) \| \
May 2017-Present) \vspace{5pt} \noindent

 \addtolength{\leftskip}{14mm}{
 \noindent Aimed at extracting non-redundant, uncorrelated and well informative features from an input Lung Cancer Dataset and deriving the right
choice of parameter initialization values in this problem of non-convex optimization.
 Obtained pen-stroke like features when implemented on MNIST database of hand-written digits, using suitable data preprocessing, greedy
layer-wise training and multiple fine-tunings of the stacked autoencoder consisting of three different cascaded autoencoder.
Verified the superior quality of feature extraction of stacked autoencoder over an autoencoder(three layered deep neural network).

}

\vspace{10pt} 

\noindent \addtolength{\leftskip}{-7mm}{
\noindent 2. Negative Capacitance FET Model 1.0.0 implementation in MATLAB\noindent \newline \hspace*{15 pt}(RTE-2017)\hspace*{5pt}(Prof. Shaloo Rakheja (NYU,USA) \| \ June 2017-July 2017) \vspace{5pt} 
 }\noindent
 
 \addtolength{\leftskip}{8mm}{
\noindent  Gained an in-depth knowledge of nanoscale MOSFETS and the device physics involved with it on nanoHUB-U. 
Understood the compact model on NCFETs involving LK equations and variation of different device parameters. 
 Extensively studied Verilog-A and translated the model implementation available in it to MATLAB. 
 Simulated the created MATLAB code for the model and compared the results with available experimental data.\vspace{10pt} 
}

 \addtolength{\leftskip}{-14mm}{
\vspace*{5pt} \noindent
\hspace*{5pt} \textbf{Awards and achievements} \newline 
\vspace{1pt} \noindent
}
  \vspace{5pt}
 \noindent \addtolength{\leftskip}{4mm}{
 
 \noindent - Secured an All India Rank of 990 among 1.5 lakh candidates who \\
 \hspace*{8pt}appeared for JEE Advanced 2015, conducted by IITs\newline - Felicitated with Academic Excellence Award(awarded to Top 10 \% of a \hspace*{6.5 pt}batch of 850 students) at IIT Kanpur for the year 2015-2016\newline - Placed on Honor Roll of SN Kansagra School for excellent academic \\ 
 \hspace*{5pt} performance in the year 2011-2012\vspace{15pt}\noindent
}

 \addtolength{\leftskip}{-4mm}{
\vspace*{5pt} \noindent
\hspace*{5pt} \textbf{Hobbies} \newline 
\vspace{1pt} \noindent
}
  \vspace{1pt}
 \noindent \addtolength{\leftskip}{4mm}{
 
 \noindent - Sports: Cricket, Chess, Football\newline - Music: Violin\newline - Cartoons: Anime
}
\end{document}




